An Evolutionary Algorithm for the Multiobjective Risk-Equity Constrained Routing Problem

### 2011-11-22 DAW_hazmatHypE/trunk/paper/hazmatRouting_EvolOptim.tex
a bit more text

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% our packages and definitions: %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{url} 
\usepackage{color}
% \usepackage{dsfont}
\usepackage{booktabs}

@@

As a test case for all the experiments, we chose to use a real-world case study based on the work of \citet{bianco09}. The network used here consists of 311 nodes and 441 arcs and represents the main transport roads in Italy's Lazio region which, amongst other cities, includes the capital Rome. We distinguish between instances with a different number of commodities (between 2 and 4) and with different numbers of trucks, see Table~\ref{tab:instances}.

\TODO{rewrite:} The risks $r_{ij}^c$ for each arc $(i,j) \in A$ and commodity $c \in C$ are evaluated as the societal risk computed as the number of people living inside the exposure zone around link $(i,j)$ (whose size depends on the hazmat type $c$ times the accident probability involving the vehicle), for details see  \citep{bianco09}.

\begin{table}
\caption{\label{tab:instances} Parameters of the instances used in the experimental analyses.}
\begin{tabular}{lllll}
	\toprule
	name & \begin{minipage}{1cm}\#com\-mod\-i\-ties\end{minipage} & \#trucks & cost range & risk range \\ \midrule
	lazio\_2\_1 & 2 & \small 20+19         & & \begin{minipage}[t]{3.7cm} \small [762, 274628]\\ x [610.18, 219702.6]\end{minipage}\\
	lazio\_2\_2 & 2 & \small 23+29         & & \\
	lazio\_3\_1 & 3 & \small 25+16+28      & & \begin{minipage}[t]{3.7cm} \small [762, 274628]\\ x [610.18, 219702.6]\\ x [1120.352, 439405.2]\end{minipage}\\
	lazio\_4\_1 & 4 & \small 21+3+30+5     & \small [0.0109239, 3.93701] & \begin{minipage}[t]{3.7cm} \small [762, 274628]\\ x [610.18, 219702.6]\\ x [1120.352, 439405.2]\\ x [762, 274628]\end{minipage}\\
	\bottomrule
\end{tabular}
\end{table}

@@

\subsection{Experimental Settings}
population size: 100, 2000 generations, 10 runs, hypervolume's reference point for HypE as in Table~\ref{tab:referencepoints} chosen according to initial objective function values: such that all initial solutions have a contribution to the hypervolume indicator (ref point the same in all objectives due to off-the-shelf PISA implementation of HypE), hypervolume computation exact

@@

\subsection{The Influence of Standard Parameters}
\begin{itemize}
	\item show exemplarily the influence of some of the standard parameters of the EMO algorithm which 
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% our packages and definitions: %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{url} 
\usepackage{color}
% \usepackage{dsfont}
\usepackage{booktabs}
\usepackage{amsmath}

@@

As a test case for all the experiments, we chose to use a real-world case study based on the work of \citet{bianco09}. The network used here consists of 311 nodes and 441 arcs and represents the main transport roads in Italy's Lazio region which, amongst other cities, includes the capital Rome. We distinguish between instances with a different number of commodities (between 2 and 4) and with different numbers of trucks, see Table~\ref{tab:instances}. While the costs $c_{ij}$ are proportional to the real distance between the two locations $i$ and $j$, the risks $r_{ij}^c$ for each arc $(i,j) \in A$ and commodity $c \in C$ have been computed as a product of the arc's length, the actual population density in the area of the arc and a constant which depends on the commodity, for details see \citep{bianco09} and Table~\ref{tab:instances}. Solely one instance is created differently: to show the impact of correlation between the costs and the risks, we created the instance lazio$_{\text ncorr}$\_4\_1 with the same graph and risks as for the instance lazio\_4\_1 but with randomly permutated costs where each occuring cost value has been divided by a random value between 0 and 5000.

\begin{table}
\caption{\label{tab:instances} Parameters of the instances used in the experimental analyses.}
\begin{tabular}{lllll}
	\toprule
	name & \begin{minipage}{1cm}\#com\-mod\-i\-ties\end{minipage} & \#trucks & cost range & risk range \\ \midrule
	lazio\_2\_1 & 2 & \small 20+19         & & \begin{minipage}[t]{3.7cm} \small [762, 274628]\\ x [610.18, 219702.6]\end{minipage}\\
	lazio\_2\_2 & 2 & \small 23+29         & & \\
	lazio\_3\_1 & 3 & \small 25+16+28      & & \begin{minipage}[t]{3.7cm} \small [762, 274628]\\ x [610.18, 219702.6]\\ x [1120.352, 439405.2]\end{minipage}\\
	lazio\_4\_1 & 4 & \small 21+3+30+5     & \small [0.25, 41] & \begin{minipage}[t]{3.7cm} \small [762, 274628]\\ x [610.18, 219702.6]\\ x [1120.352, 439405.2]\\ x [762, 274628]\end{minipage}\\
	lazio$_{\text uncorr}$\_4\_1 & 4 & \small 21+3+30+5     & \small [0.0109239, 3.93701] & \begin{minipage}[t]{3.7cm} \small [762, 274628]\\ x [610.18, 219702.6]\\ x [1120.352, 439405.2]\\ x [762, 274628]\end{minipage}\\
	\bottomrule
\end{tabular}
\end{table}

@@

\subsection{Experimental Settings}
Except otherwise stated, we used the following parameter setting. We perform 10 independent runs of HypE for 2000 generations with a population size of 100. The reference point for the hypervolume indicator was chosen as in Table~\ref{tab:referencepoints} according to the initial objective function values, such that all initial solutions have a positive contribution to the hypervolume indicator\footnote{Note that the reason for using the same values in all objectives is the used PISA implementation of HypE.}. In all cases, the hypervolume computation is exact.

@@

\subsection{Changing the Population Size}
In a second experiment, we show that changing the population size of the algorithm in standard ranges does not change the algorithm outcome drastically.
\TODO{write}

\subsection{Changing the Environmental Selection}
With a last experiment, we show the influence of the algorithm's environmental selection scheme on the performance and in particular how this can be used to steer the search towards specific regions of the Pareto front.
\TODO{write}
